---
title: "R Notebook"
author: "Kiki Kanik"
output: html_notebook
---
Part I:
1)Mean, variance, moments and median are all properties of exponential distribution.

a) the mean refers to a value that is expected to occur. In this sense, it is E(x)= 1/lambda

b)the variance is 1/(lambda^2). The standard deviation is equal to the mean. 

Part II:
2) when rate is 1: Mean (1.042173) SD (1.006045)
```{r}
exp.draws.1 = rexp(n=200)
mean(exp.draws.1)
sd(exp.draws.1)
```
3)
when rate is 0.1: Mean (10.98142) SD (12.39049)
```{r}
exp.draws.0.1 = rexp(n=200, rate=0.1)
mean(exp.draws.0.1)
sd(exp.draws.0.1)
```

when rate is 0.5: Mean (1.731437) SD (1.068284)
```{r}
exp.draws.0.5 = rexp(n=10, rate=0.5)
mean(exp.draws.0.5)
sd(exp.draws.0.5)
```
when rate is 5: Mean (0.2694435) SD (0.2341035)
```{r}
exp.draws.5 = rexp(n=10, rate=5)
mean(exp.draws.5)
sd(exp.draws.5)
```
when rate is 10: Mean (0.09598443) SD (0.07485583)
```{r}
exp.draws.10 = rexp(n=10, rate=10)
mean(exp.draws.10)
sd(exp.draws.10)
```
4) a. 
```{r}
hist(exp.draws.1)
```
b) 
```{r}
plot(exp.draws.1)
```
4c) 
```{r}
plot(exp.draws.1, exp.draws.0.1)
```
5)
you are seeing that the mean and variance are both 1/λ and
the mean versus the standard deviation is a straight line since the mean is equal to the standard deviation.
```{r}
means = c(mean(exp.draws.0.1), mean(exp.draws.0.5), mean(exp.draws.1), mean(exp.draws.5), mean(exp.draws.10))
rates = c(0.1, 1, 0.5, 5, 10)
sds = c(sd(exp.draws.0.1), sd(exp.draws.0.5), sd(exp.draws.1), sd(exp.draws.5), sd(exp.draws.10))
```
a. This plots the relationship between the means and the rates. 
```{r}
plot(means, rates)
```
b. This plots the relationship between the standard deviations and the rates.
```{r}
plot(sds, rates)
```
c. This graph represents the relationship between the means and sds. 
```{r}
plot(means, sds)
```

6)
a. 
```{r}
big.exp.draws.1=(rexp(n=1100000))
mean(big.exp.draws.1)
sd(big.exp.draws.1)
```
b)
```{r}
mbto= mean(big.exp.draws.1[which(big.exp.draws.1>1)])
```
c)
```{r}
?matrix
```
i. data = a data vector
ii. nrow = the number of rows wanted
iii. ncol = the number of colomns wanted
iv. byrow = FALSE is default, and the matrix is filled with colomns. If TRUE, matrix is filled by rows.
d)
hist() created a histogram with the data retreived from the matrix
```{r}
big.exp.draws.1.mat = matrix(big.exp.draws.1,1100,1000)
dim(big.exp.draws.1.mat)
hist(big.exp.draws.1.mat)
```
e) 
```{r}
?apply
```
f) 
```{r}
x <- cbind(x1 = 3, x2 = c(4:1, 2:5))
dimnames(x)[[1]] <- letters[1:8]
apply(x, 2, mean, trim = .2)
col.sums <- apply(x, 2, sum)
row.sums <- apply(x, 1, sum)
rbind(cbind(x, Rtot = row.sums), Ctot = c(col.sums, sum(col.sums)))

stopifnot( apply(x, 2, is.vector))
```
g)
```{r}
sample.means <- colMeans(big.exp.draws.1.mat)
```
